### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Added line to load sqldf package

Working with the Long Data and heading to an AR model
========================================================

Load in data
```{r}
load("~/Forecast-Peak-With-Google-Trends/LongWtrends.RData")
summary(LongWtrends)
```

>>>>

Working with the Long Data and heading to an AR model
=======================================================
library("sqldf")
Load in data
```{r}
load("~/Forecast-Peak-With-Google-Trends/LongWtrends.RData")
summary(LongWtrends)
```
